A Parallel General Purpose Multi-Objective Optimization Framework, with Application To Beam Dynamics

### 2018-04-11 paper/theor-experiment.tex
paper changes

\subsubsection{AWA Optimization Results}
Given the parameters and variable boundaries in Section \ref{awaproblem}, 
four optimization experiments were done with varying GA parameters, see Table \ref{extable}.
From here on, we will reference each experiment as ex-1, ex-2, ex-3 and ex-4. 
They were each allowed to run for twenty four hours. 
Similar to the time step scan, the goal of this exercise was to determine which set of optimization
parameters strongly influence the results, and whether there was a time to solution
difference.

\begin{table}%[h!]
	\begin{center}
		\caption{Input Parameters for initial twenty four hour AWA optimization experiments. 
			The gene mutation probability was equal to the mutation probability (not shown) in all four experiments.}
		\label{extable}
		\begin{tabular*}{\textwidth}{l @{\extracolsep{\fill}} C C D }
			\hline\noalign{\smallskip}
			& Gene Mutation Probability & Recombination Probibility & Number of completed generations \\
			\noalign{\smallskip}\hline\noalign{\smallskip}
			ex-1 &  0.1  & 0.9  &  96 \\
			ex-2 &  0.3  & 0.7  &  81 \\
			ex-3 &  0.8  & 0.2  &  53 \\
			ex-4 &  0.01 & 0.09 &  95 \\
			\noalign{\smallskip}\hline
		\end{tabular*}
	\end{center}
\end{table}

>>>>

\subsubsection{AWA Optimization Results}
While the optimization problem and goals are well defined (Section \ref{awaproblem}), 
it is not clear what the best input parameters for the NSGA-II are.
These parameters include gene mutation probability, mutation probability, 
recombination probability, number of individuals (initial and independent), and number of generations. 
Given the beam line and design variables given in Section \ref{awaproblem}, 
four optimization experiments were done with varying NSGA-II parameters, see Table \ref{extable}. 
\begin{table}%[h!]
	\begin{center}
		\caption{Input Parameters for initial twenty four hour AWA optimization experiments. 
			The gene mutation probability was equal to the mutation probability (not shown) in all four experiments. The number of individuals}
		\label{extable}
		\begin{tabular*}{\textwidth}{l @{\extracolsep{\fill}} C C D }
			\hline\noalign{\smallskip}
			& Gene Mutation Probability & Recombination Probibility & Number of completed generations \\
			\noalign{\smallskip}\hline\noalign{\smallskip}
			ex-1 &  0.1  & 0.9  &  96 \\
			ex-2 &  0.3  & 0.7  &  81 \\
			ex-3 &  0.8  & 0.2  &  53 \\
			ex-4 &  0.01 & 0.09 &  95 \\
			\noalign{\smallskip}\hline
		\end{tabular*}
	\end{center}
\end{table} 
From here on, we will reference each experiment as ex-1, ex-2, ex-3, and ex-4. 
The initial number of individuals was fixed at 656, 
and the number of independent individuals per generation was fixed at 328. 
These numbers we in part based on the architecture of the KNL's. 
Since each simulation takes 8 cores, and there are 64 cores per KNL node, 
we wanted a large population size that would fit evenly on these resources. 
We also reduced the number of objectives to the four most important for quicker evaluation of these tests.
These objectives include: 
$\epsilon_{x, s_1}\text{, } \epsilon_{x, s_2}\text{, } \text{rms}_{s, s_1}\text{, and }  \text{rms}_{s, s_2}$
The optimization in the OPAL input file was defined as follows:
\vspace{0.2cm}
{\footnotesize \begin{verbatim}
	dv0: DVAR, VARIABLE="IBF",    LOWERBOUND=200.0, UPPERBOUND=500.0;
	dv1: DVAR, VARIABLE="IM",     LOWERBOUND=170.0, UPPERBOUND=260.0;
	dv2: DVAR, VARIABLE="GPHASE", LOWERBOUND=-30.0, UPPERBOUND=0.0;
	dv3: DVAR, VARIABLE="FWHM",   LOWERBOUND=1.5,   UPPERBOUND=10.0;

	// Quad values
	dv4: DVAR, VARIABLE="KQ1", LOWERBOUND=-8.0, UPPERBOUND=8.0;
	dv5: DVAR, VARIABLE="KQ2", LOWERBOUND=-8.0, UPPERBOUND=8.0;
	dv6: DVAR, VARIABLE="KQ3", LOWERBOUND=-8.0, UPPERBOUND=8.0;
	dv7: DVAR, VARIABLE="KQ4", LOWERBOUND=-8.0, UPPERBOUND=8.0;

	rmss1:  OBJECTIVE,EXPR="fabs(statVariableAt('rms_s',16.5))";
	emitx1: OBJECTIVE,EXPR="fabs(statVariableAt('emit_x',16.5))";

	rmss2:  OBJECTIVE,EXPR="fabs(statVariableAt('rms_s',18.5))";
	emitx2: OBJECTIVE,EXPR="fabs(statVariableAt('emit_x',18.5))";
	\end{verbatim}}
\vspace{0.2cm}

They were each allowed to run for twenty four hours. 
Similar to the time step scan, the goal of this exercise was to determine which set of optimization
parameters strongly influence the results, and whether there was a time to solution
difference.
